### 2024-09-26 manuscript.tex
Various improvements

The data sources contained ceilometer observations captured by the Vaisala CL51
and CL31 operating at a wavelenght of 910 nm and the Lufft CHM-15k operating at
1064 nm, described in detail below (Sections \ref{sec:cl51} and
\ref{sec:chm15k}). A ceilometer is a low-power near-infrared vertically
pointing lidar with the purpose of measuring the cloud base, but it also
measures the full vertical structure of clouds as long as the laser signal is
not attenuated by thick clouds, which can be used to infer additional
information such as a cloud mask and cloud occurrence by height.

@@

\begin{table}[p!]
% TODO: Add sampling intervals.
\caption{
An overview of the analysed voyages, campaigns and stations. Start, end, and days
(UTC; inclusive) indicate the time period when the vessel was south of 40°S.
Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South
America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is
rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate
CL31.
}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
\textbf{Name} & \textbf{Vessel or station} & \textbf{Ceil.} & \textbf{Region} & \textbf{Start} & \textbf{End} & \textbf{Days}\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124 \\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CL31    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
MICRE    & Macquarie Is. station         & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

@@

\subsection{Vaisala CL51 and CL31}
\label{sec:cl51}

The Vaisala CL51 (photo in Fig. \ref{fig:map}d) and CL31 are ceilometers
operating at a near-infrared wavelength of 910 nm. The maximum range is 15.4 km
(CL51), 7.7 km (CL31 with 5 m vertical resolution), and 7.550 km (CL31 with 10
m vertical resolution). The vertical resolution is 10 m (5 m configurable), and
the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s (RV
\emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS campaign, unlike raw
instrument data available for the other voyages and stations, the Vaisala CL31
data were made available by the Atmospheric Radiation Measurement (ARM)
processed to a maximum range of 7.545 km, a vertical resolution of 30 m, and
sampling resolution of 16 s. The wavelength of 910 nm is affected by water
vapour absorption of about 20\% in the mid-latitudes
\citep{wiegner2015,wiegner2019}.  The instrument data files containing raw
uncalibrated backscatter were first converted to NetCDF with cl2nc
(\url{https://github.com/peterkuma/cl2nc}) and then processed with the ALCF
(Section \ref{sec:alcf}) to produce absolutely calibrated attenuated volume
backscattering coefficinet (AVBC), cloud mask, cloud occurrence by height and
the total cloud fraction. CL51 can also be configured to emulate CL31. The
Vaisala CL51 and CL31 instruments were used on most of the voyages and stations
analysed here. Fig. \ref{fig:example}a shows an example of derived from the
CL51 instrument.

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, AA15-16 dataset provided by the
Australian Antarctic Division (AAD) and University of Canterbury (UC), RV
\emph{Tangaroa} datasets provided by the National Institute of Water and
Atmospheric Research and UC, RV \emph{Nathaniel B. Palmer} dataset provided
by the National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and UC, HMNZS \emph{Wellington}
dataset provided by the Royal New Zealand Navy and UC, the MARCUS dataset was
provided by the Atmospheric Radiation Measurement (ARM). The MICRE dataset was
provided by ARM, the Australian Bureau of Meteorology, AAD and UC.  We thank
the scientific staff, the crew, and everyone involved in collecting data on the
voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
Harvey (†), Simon P.  Alexander and Alex Schuddeboom. We acknowledge the ICON
model output provided by the nextGEMS project and the Deutsches
Klimarechenzentrum (DKRZ), reanalysis dataset ERA5 provided by the Copernicus
Climate Change Service and MERRA-2 provided by the Global Modeling and
Assimilation Office. We dedicate this study to the memory of Mike J. Harvey,
who very substantially contributed to obtaining atmospheric measurments on the
RV \emph{Tangaroa} voyages used in this study.

@@

The RV \emph{Polarstern} datasets are openly available from Pangaea
(\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available
from the NASA Goddard Earth Sciences (GES) Data and Information Services Center
(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
data are openly available from the Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
Levante cluster of the DKRZ
(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
\url{https://luv.dkrz.de/register/}. The CERES products are available from the
project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).
The TAN1802 data ara available on Zenodo
(\url{https://doi.org/10.5281/zenodo.4060237}).  The other voyage and station
data are openly available on Zenodo (). Subsetted model and reanalysis data for
the voyage tracks and the station and data processed with the ALCF are openly
available on Zenodo ().

@@

TODO

>>>>

The data sources contained ceilometer observations captured by the Vaisala CL51
operating at a wavelenght of 910 nm and the Lufft CHM-15k operating at
1064 nm, described in detail below (Sections \ref{sec:cl51} and
\ref{sec:chm15k}). A ceilometer is a low-power near-infrared vertically
pointing lidar with the purpose of measuring the cloud base, but it also
measures the full vertical structure of clouds as long as the laser signal is
not attenuated by thick clouds, which can be used to infer additional
information such as a cloud mask and cloud occurrence by height.

@@

\begin{table}[p!]
% TODO: Add sampling intervals.
\caption{
An overview of the analysed voyages, campaigns and stations. Start, end, and days
(UTC; inclusive) indicate the time period when the vessel was south of 40°S.
Abbreviations: ceilometer (ceil.), Australia (AU), New Zealand (NZ), South
America (SA), Atlantic Ocean (AO) and Africa (AF). The number of days is
rounded to the nearest integer. CL51/31 indicates CL51 configured to emulate
CL31.
}
\label{tab:voyages}
\small
\begin{tabular}{llllllr}
\textbf{Name} & \textbf{Vessel or station} & \textbf{Ceil.} & \textbf{Region} & \textbf{Start} & \textbf{End} & \textbf{Days}\\
\hline
AA15-16  & RSV \emph{Aurora Australis}   & CL51    & AU       & 2015-10-22 & 2016-02-22 & 124 \\
HMNZSW16 & HMNZS \emph{Wellington}       & CHM 15k & NZ       & 2016-11-23 & 2016-12-19 & 27 \\
MARCUS   & RSV \emph{Aurora Australis}   & CL51    & AU       & 2017-10-29 & 2018-03-26 & 149 \\
MICRE    & Macquarie Is. station         & CL51    & AU/NZ    & 2016-04-03 & 2018-03-14 & 710 \\
NBP1704  & RV \emph{Nathaniel B. Palmer} & CHM 15k & NZ       & 2017-04-14 & 2017-06-08 & 55 \\
PS77/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2010-12-01 & 2011-02-04 & 65 \\
PS77/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-02-07 & 2011-04-14 & 66 \\
PS79/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2011-12-06 & 2012-01-02 & 27 \\
PS79/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-01-10 & 2012-03-10 & 61 \\
PS79/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-03-14 & 2012-04-08 & 26 \\
PS81/2   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2012-12-02 & 2013-01-18 & 47 \\
PS81/3   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-01-22 & 2013-03-17 & 55 \\
PS81/4   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-03-18 & 2013-04-16 & 30 \\
PS81/5   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-04-20 & 2013-05-23 & 33 \\
PS81/6   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-06-10 & 2013-08-12 & 63 \\
PS81/7   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-08-15 & 2013-10-14 & 60 \\
PS81/8   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-11-12 & 2013-12-14 & 31 \\
PS81/9   & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2013-12-21 & 2014-03-02 & 71 \\
PS89     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2014-12-05 & 2015-01-30 & 56 \\
PS96     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2015-12-08 & 2016-02-14 & 68 \\
PS97     & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-02-15 & 2016-04-06 & 52 \\
PS103    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2016-12-18 & 2017-02-02 & 46 \\
PS104    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2017-02-08 & 2017-03-18 & 39 \\
PS111    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-01-21 & 2018-03-14 & 52 \\
PS112    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-03-18 & 2018-05-05 & 49 \\
PS117    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2018-12-18 & 2019-02-07 & 51 \\
PS118    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2019-02-18 & 2019-04-08 & 50 \\
PS123    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-01-10 & 2021-01-31 & 21 \\
PS124    & RV \emph{Polarstern}          & CL51    & SA/AO/AF & 2021-02-03 & 2021-03-30 & 55 \\
TAN1502  & RV \emph{Tangaroa}            & CL51/31 & NZ       & 2015-01-20 & 2015-03-12 & 51 \\
TAN1702  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2017-03-09 & 2017-03-31 & 23 \\
TAN1802  & RV \emph{Tangaroa}            & CHM 15k & NZ       & 2018-02-07 & 2018-03-20 & 41 \\
\hline
\textbf{Total} &                         &         &          &            &            & \textbf{2421}\\
\end{tabular}
\normalsize
\end{table}

@@

\subsection{Vaisala CL51}
\label{sec:cl51}

The Vaisala CL51 (photo in Fig. \ref{fig:map}d) is a ceilometer operating at a
near-infrared wavelength of 910 nm. CL51 can also be configured to emulate the
Vaisala CL31. The maximum range is 15.4 km (CL51), 7.7 km (CL31 emulation mode
with 5 m vertical resolution), and 7.550 km (CL31 emulation mode with 10 m
vertical resolution). The vertical resolution is 10 m (5 m configurable), and
the sampling (temporal) resolution is 6 s (AA15‐16, MARCUS, and MICRE), 36 s
(RV \emph{Polarstern}), and about 2.37 s (TAN1502). From the MARCUS and MICRE
campaigns, unlike raw instrument data available for the other voyages and
stations, the Vaisala CL51 data were made available by the Atmospheric
Radiation Measurement (ARM) processed to a maximum range of 7.545 km, a
vertical resolution of 30 m, and sampling resolution of 16 s. The wavelength of
910 nm is affected by water vapour absorption of about 20\% in the
mid-latitudes \citep{wiegner2015,wiegner2019}.  The instrument data files
containing raw uncalibrated backscatter were first converted to NetCDF with
cl2nc (\url{https://github.com/peterkuma/cl2nc}) and then processed with the
ALCF (Section \ref{sec:alcf}) to produce absolutely calibrated attenuated
volume backscattering coefficinet (AVBC), cloud mask, cloud occurrence by
height and the total cloud fraction.  The Vaisala CL51 instruments were used on
most of the voyages and stations analysed here. Fig. \ref{fig:example}a shows
an example of derived from the CL51 instrument.

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic
Division (AAD) and University of Canterbury (UC), RV \emph{Tangaroa} datasets
provided by the National Institute of Water and Atmospheric Research and UC,
the NBP1704 dataset provided by the National Science Foundation, Cooperative
Institute for Research in Environmental Sciences, University of Colorado and
UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the
MARCUS dataset provided by the Atmospheric Radiation Measurement (ARM), AAD and
UC, and the MICRE dataset provided by ARM, the Australian Bureau of
Meteorology, AAD and UC. We thank the scientific staff, the crew, and everyone
involved in collecting data on the voyages and stations, especially Kelly
Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally
Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander
and Alex Schuddeboom. We acknowledge the ICON model output provided by the
nextGEMS project and the Deutsches Klimarechenzentrum (DKRZ), reanalysis
dataset ERA5 provided by the Copernicus Climate Change Service and MERRA-2
provided by the Global Modeling and Assimilation Office. We dedicate this study
to the memory of Mike J. Harvey, who very substantially contributed to
obtaining atmospheric measurments on the RV \emph{Tangaroa} voyages used in
this study.

@@

The RV \emph{Polarstern} datasets are openly available on Pangaea
(\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available
from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available
from the NASA Goddard Earth Sciences (GES) Data and Information Services Center
(DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}).  The ERA5
data are openly available from the Copernicus Climate Data Store (CDS)
(\url{https://cds.climate.copernicus.eu}). The ICON data are available on the
Levante cluster of the DKRZ
(\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at
\url{https://luv.dkrz.de/register/}. The CERES products are available from the
project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric
Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}).  The
TAN1802 data ara available on Zenodo
(\url{https://doi.org/10.5281/zenodo.4060237}).  The other voyage and station
data are openly available on Zenodo ([TODO]). Subsetted model and reanalysis data
for the voyage tracks and the station and data processed with the ALCF are
openly available on Zenodo ([TODO]).

@@

[TODO]
